kableExtraTutorial

### 2017-08-29 rmd_tutorial.rmd
remove the swd argument
git output

---
title: "kableExtraTutorial"
author: "April"
date: "August 29, 2017"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
#install.packages("kableExtra")

# For dev version
# install.packages("devtools")
#devtools::install_github("haozhu233/kableExtra")
```

```{r}
library(knitr)
library(kableExtra)
dt <- mtcars[1:5, 1:6]

setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")

@@

```{r}
kable(dt)

kable(head(MLH1_data) )
```
```{r}
##FIX ORDER HERE
MLH1_data$strain<- factor(MLH1_data$strain,levels =c("G", "LEWES",
                                     "WSB", "PWD","MSM","CAST"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)
library(dplyr)
MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(file.name = factor(file.name)) #another category that you want the order to match

@@

```{r}
#Quality / number of passing mice
q_cutoff_table <- ddply(MLH1_data, .(mouse), summarise,
                        total =  length(nMLH1.foci),
                        q5 = sum(as.numeric(quality) >= 4, na.rm = TRUE ), 
                        q_l3 = sum(as.numeric(as.numeric(quality)) <= 4, na.rm = TRUE )
)
#q_cutoff_table

>>>>

---
title: "kableExtraTutorial"
author: "April"
date: "August 29, 2017"
output: github_document
---

```{r}
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(dplyr)
dt <- mtcars[1:5, 1:6]

#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")

@@

```{r}
##FIX ORDER HERE
MLH1_data$strain<- factor(MLH1_data$strain,levels =c("G", "LEWES",
                                     "WSB", "PWD","MSM","CAST"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)
library(dplyr)
MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(file.name = factor(file.name)) #another category that you want the order to match

@@

```{r}
#Quality / number of passing mice
q_cutoff_table <- ddply(MLH1_data, .(mouse), summarise,
                        total =  length(nMLH1.foci),
                        q5 = sum(as.numeric(quality) >= 4, na.rm = TRUE ), 
                        q_l3 = sum(as.numeric(as.numeric(quality)) <= 4, na.rm = TRUE )
)
q_cutoff_table
